Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
tables repositioned
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60857 72bbbca6-d526-0410-a7d9-f06f51895060
what I've done so far
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60860 72bbbca6-d526-0410-a7d9-f06f51895060
Wefwef
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60862 72bbbca6-d526-0410-a7d9-f06f51895060
fixed makefile
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60863 72bbbca6-d526-0410-a7d9-f06f51895060
some more stuff
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60867 72

\documentclass[a4paper,11pt, onecolumn]{article}

@@

@@

@@

%\usepackage{times}
\setmainfont{Times New Roman}

\newcommand{\tag}[1]{\texttt{‹#1›}}

@@

@@

\maketitleabstract{}
\thispagestyle{firststyle}

@@

\subsection{Kazakh}

@@

\begin{table}
  \centering
\begin{small}
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    UN Declaration on Human Rights & Legal text on human rights & 25 & 409 & 16.3 \\
    Phrasebook                     & Phrases from Wikitravel   & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз             & Philosophical text        & 34 & 525 & 15.4 \\ 
    Қожанасырдың тойға баруы       & Folk tale from Wikisource  & 8 & 140 & 17.5 \\
    Ер Төстік                      & Folk tale from Wikisource  & 23 & 203 & 8.8 \\
    Азамат қайда?                  & Story for language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014 & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran)                                & 111 & 1562 & 14.0 \\
    Радиан & Wikipedia article (Radian)                            & 2 & 17 & 8.5 \\
    \hline
    \multicolumn{2}{c|}{~} & 302 & 3741 & 12.3 \\\cline{3-5}
  \end{tabular}
\end{small}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types from 
    free and public-domain sources.}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Label} & \textbf{Description} \\

@@

@@

@@

>>>>

\documentclass[a4paper,11pt, onecolumn,twoside]{article}

@@

%%%%% Language and font stuff %%%%%

@@

%\usepackage{times}
\setmainfont{Times New Roman}
\newfontfamily\udfont[Scale=MatchLowercase,Letters=SmallCaps]{Linux Libertine O}

%%%%% General formatting stuff %%%%%

@@

%%%%% Stuff for this paper %%%%%
\usepackage{tikz-dependency}
\newcommand{\gmk}[1]{\texttt{#1}}
\newcommand{\tag}[1]{\texttt{‹#1›}}
\newcommand{\udtag}[1]{\texttt{@#1}}
\newcommand{\udlabel}[1]{{\udfont #1}}
%\newcommand{\corrauthor}[1]{\footnotemark\footnotetext{hargle}}

%%%%% Paper metadata %%%%%

@@

%%%%% End preamble %%%%%

@@

%\thanks{hargle}
\maketitleabstract{}
\thispagestyle{firststyle}

@@

\subsection{Kazakh}\label{sec:kazakh}

@@

\begin{table}[htbp]
  \centering
\begin{small}
  \begin{tabular}{|l|l|r|r|r|}
    \hline
    \textbf{Document} & \textbf{Description} & \textbf{Sentences} & \textbf{Tokens} & \textbf{Avg. length}\\
    \hline
    UN Declaration on Human Rights & Legal text on human rights & 25 & 409 & 16.3 \\
    Phrasebook                     & Phrases from Wikitravel   & 37 & 205 & 5.5 \\
    Жиырма Бесінші Сөз             & Philosophical text        & 34 & 525 & 15.4 \\ 
    Қожанасырдың тойға баруы       & Folk tale from Wikisource  & 8 & 140 & 17.5 \\
    Ер Төстік                      & Folk tale from Wikisource  & 23 & 203 & 8.8 \\
    Азамат қайда?                  & Story for language learners & 48 & 434 & 9.0 \\
    Футболдан әлем чемпионаты 2014 & Wikipedia article (2014 World Cup) & 14 & 246 & 17.5 \\
    Иран & Wikipedia article (Iran)                                & 111 & 1562 & 14.0 \\
    Радиан & Wikipedia article (Radian)                            & 2 & 17 & 8.5 \\
    \hline
    \multicolumn{2}{c|}{~} & 302 & 3741 & 12.3 \\\cline{3-5}
  \end{tabular}
\end{small}
  \caption{Composition of the corpus. The corpus covers a range of genres and text types from 
    free and public-domain sources.}
\end{table}

@@

\begin{table}[htbp]
  \centering
  \begin{tabular}{|l|l|}
    \hline
    \textbf{Label} & \textbf{Description} \\

@@

Some nominals occur together to act as a single nominal.

One example of this is indefinite genitives.  In such constructions, a ``modifying'' nominal is morphologically not marked (which means it will be tagged as \tag{nom}, as discussed in §\ref{sec:kazakh}), though should be considered an indefinite genitive.  The modified element is a nominal with third-person possessive morphology, an example of which is provide in figure~\ref{fig:indefgen}.

\begin{figure}[htbp]
	\centering
	\begin{dependency}[theme = simple, font = \small]
	   \begin{deptext}[column sep=0.3cm]
			әлем \& чемпионаты \\
			\gmk{n.nom} \& \gmk{n.px3sg.nom} \\
		\end{deptext}
		\depedge{1}{2}{\udlabel{nmod}}
	\end{dependency}
	\caption{A nominal depending on an indefinite genitive.}\label{fig:indefgen}
\end{figure}

In these examples, the indefinite genitive is considered \udtag{nmod}.

@@

\cite{ballesteros15}, \cite{nivre07}

@@

%Tolgonay?, Aida?
